Multi-reference pangenome graphs

### 2022-01-08 manuscript/fig_induction.tex
figure 1 now with colored paths

%Lines
\draw[very thick,color=red] (seqA1) -- (seqA2);
\draw[very thick,color=red] (seqA2) -- (seqA3);
\draw[very thick,color=red] (seqA3) -- (seqA4);
\draw[very thick,color=red] (seqA4) -- (seqA5);
\draw[very thick,color=red] (seqA5) -- (seqA6);
\draw[very thick,color=red] (seqA6) -- (seqA7);

\draw[very thick,color=green] (seqB1) -- (seqB2);
\draw[very thick,color=green] (seqB2) -- (seqB3);
\draw[very thick,color=green] (seqB3) -- (seqB4);
\draw[very thick,color=green] (seqB4) -- (seqB5);
\draw[very thick,color=green] (seqB5) -- (seqB6);
\draw[very thick,color=green] (seqB6) -- (seqB7);

\draw[very thick,color=blue] (seqC1) -- (seqC2);
\draw[very thick,color=blue] (seqC2) -- (seqC3);
\draw[very thick,color=blue] (seqC3) -- (seqC4);
\draw[very thick,color=blue] (seqC4) -- (seqC5);

@@

\draw[very thick] (g1) to (g2);
\draw[very thick] (g1) to (g3);
\draw[very thick] (g2) to (g4);
\draw[very thick] (g3) to (g4);
\draw[very thick] (g4) to (g5);
\draw[very thick] (g4) to [looseness=1] (g7);
\draw[very thick] (g5) to (g6);
\draw[very thick] (g6) to (g7);
\draw[very thick] (g7) to (g8);
\draw[very thick] (g7) to (g9);

@@

\node[pathnode,label=left:path1] (pathA1) [below = 1cm of g1] {1};
\node[pathnode] (pathA2) [right of=pathA1] {2};
\node[pathnode] (pathA3) [right of=pathA2] {3};
\node[pathnode] (pathA4) [right of=pathA3] {4};
\node[pathnode] (pathA5) [right of=pathA4] {5};
\node[pathnode] (pathA6) [right of=pathA5] {6};
\node[pathnode] (pathA7) [right of=pathA6] {7};

@@

\draw[very thick] (pathC1) -- (pathC2);
\draw[very thick] (pathC2) -- (pathC3);
\draw[very thick] (pathC3) -- (pathC4);
\draw[very thick] (pathC4) -- (pathC5);

>>>>

%Lines
\draw[line width=2.0,color=red] (seqA1) -- (seqA2);
\draw[line width=2.0,color=red] (seqA2) -- (seqA3);
\draw[line width=2.0,color=red] (seqA3) -- (seqA4);
\draw[line width=2.0,color=red] (seqA4) -- (seqA5);
\draw[line width=2.0,color=red] (seqA5) -- (seqA6);
\draw[line width=2.0,color=red] (seqA6) -- (seqA7);

\draw[line width=2.0,color=green] (seqB1) -- (seqB2);
\draw[line width=2.0,color=green] (seqB2) -- (seqB3);
\draw[line width=2.0,color=green] (seqB3) -- (seqB4);
\draw[line width=2.0,color=green] (seqB4) -- (seqB5);
\draw[line width=2.0,color=green] (seqB5) -- (seqB6);
\draw[line width=2.0,color=green] (seqB6) -- (seqB7);

\draw[line width=2.0,color=blue] (seqC1) -- (seqC2);
\draw[line width=2.0,color=blue] (seqC2) -- (seqC3);
\draw[line width=2.0,color=blue] (seqC3) -- (seqC4);
\draw[line width=2.0,color=blue] (seqC4) -- (seqC5);

@@

\begin{pgfonlayer}{bg}    % select the background layer
\draw[line width=2,transform canvas={yshift=0.05cm},color=red] (g1) to (g2);
\draw[line width=2,transform canvas={yshift=-0.05cm},color=blue] (g1) to (g2);
\draw[line width=2,transform canvas={yshift=0cm},color=green] (g1) to (g3);
\draw[line width=2,transform canvas={yshift=0cm},color=green] (g3) to (g4);
\draw[line width=2,transform canvas={yshift=0.05cm},color=red] (g2) to (g4);
\draw[line width=2,transform canvas={yshift=-0.05cm},color=blue] (g2) to (g4);
\draw[line width=2,transform canvas={yshift=0.05cm},color=red] (g4) to (g5);
\draw[line width=2,transform canvas={yshift=-0.1cm},color=blue,looseness=1] (g4) to (g7);
\draw[line width=2,transform canvas={yshift=-0.05cm},color=green] (g4) to (g5);
\draw[line width=2,transform canvas={yshift=0.05cm},color=red] (g5) to (g6);
\draw[line width=2,transform canvas={yshift=-0.05cm},color=green] (g5) to (g6);
\draw[line width=2,transform canvas={yshift=0.05cm},color=red] (g6) to (g7);
\draw[line width=2,transform canvas={yshift=-0.05cm},color=green] (g6) to (g7);
\draw[line width=2,transform canvas={yshift=0.05cm},color=red] (g7) to (g8);
\draw[line width=2,transform canvas={yshift=-0.05cm},color=blue] (g7) to (g8);
\draw[line width=2,transform canvas={yshift=0cm},color=green] (g7) to (g9);

\end{pgfonlayer}

\begin{comment}
\draw[very thick] (g1) to (g2);
\draw[very thick] (g1) to (g3);
\draw[very thick] (g2) to (g4);
\draw[very thick] (g3) to (g4);
\draw[very thick] (g4) to (g5);
\draw[very thick] (g4) to [looseness=1] (g7);
\draw[very thick] (g5) to (g6);
\draw[very thick] (g6) to (g7);
\draw[very thick] (g7) to (g8);
\draw[very thick] (g7) to (g9);
\end{comment}

%\coordinate[yshift=-0.6cm, right=0.1cm of A1.east] (aux2);

@@

\begin{comment}
\node[pathnode,label=left:path1] (pathA1) [below = 1cm of g1] {1};
\node[pathnode] (pathA2) [right of=pathA1] {2};
\node[pathnode] (pathA3) [right of=pathA2] {3};
\node[pathnode] (pathA4) [right of=pathA3] {4};
\node[pathnode] (pathA5) [right of=pathA4] {5};
\node[pathnode] (pathA6) [right of=pathA5] {6};
\node[pathnode] (pathA7) [right of=pathA6] {7};

@@

\draw[very thick] (pathC1) -- (pathC2);
\draw[very thick] (pathC2) -- (pathC3);
\draw[very thick] (pathC3) -- (pathC4);
\draw[very thick] (pathC4) -- (pathC5);
\end{comment}
